\documentclass[10pt,a4paper]{protocol}
\usepackage{amssymb,amsmath,amsfonts,eurosym,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,pdflscape,subfigure,array}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Bright}{HTML}{58318f}
\definecolor{Green}{HTML}{319866}
\definecolor{Black}{HTML}{111111}
\definecolor{LightGrey}{HTML}{515c50}

\definecolor{main}{HTML}{00274C}
\definecolor{background}{HTML}{EFF0F1}

\definecolor{alert}{HTML}{CC6600}
\definecolor{example}{HTML}{00274C}

\colorlet{heading}{main}
\colorlet{accent}{alert}
\colorlet{emphasis}{main}
\colorlet{body}{main}


% Change the bullets for itemize and rating marker
% for \risk if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faSpinner}

%% sample.bib contains your publications
\addbibresource{sample.bib}

\begin{document}
\name{Difference-in-Differences}
\tagline{Twice as good as a single difference}
\made{August 7, 2020}
\logo{6.5cm}{"rosslogo"}



\docinfo{%
  % can add more \addedtopeople
  \madeby{Sarah Miller}{mille@umich.edu}{for BE 887}
%  \addedto{John Smith}{abv1@uni.ac.uk}{October 3, 2017}
}


%\purpose{
%Difference-in-differences compares the change in an outcome in treated units before and after receiving the treatment to the change in the outcome in untreated units over the same time period. 
%} % add a short discription of the purpose for this protocol


%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makeheader
\end{fullwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \need.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \need title in the "main" bar.
Difference-in-differences compares the change in an outcome in treated units before and after receiving the treatment to the change in the outcome in untreated units over the same time period.


\need[materials]{When to use}
\req{1}{Some units are treated and some are not}{}
\begin{itemize}
	\item E.g., some states enact a policy and others do not, some workers receive a training and others do not, etc.
	\item You observe data before and after treatment for types of units.
	\item ``Spillovers'' or ``externalities'' are negligible (i.e. untreated units not affected by treatment).
\end{itemize}
\divider

\req{2}{Treated units may vary in terms of levels but are on the same trends prior to the policy}{}
\begin{itemize}
	\item It is reasonable to expect that after accounting for level differences, the untreated units capture how the treated units' outcome would have evolved in the absence of treatment.
\end{itemize}
\divider

\need[]{What to Do: The Basics}

\step{1}{Plot data of treated and untreated units against time}{40}
\begin{itemize}
	\item Ideally all treated units are treated at the same time.
	\item Do you observe a trend break in the raw data?
	\item Do treated and untreated units appear to be on a similar trend before the treatment, but diverge after the treatment?
\end{itemize}
\divider

\step{2}{``Event Study'' Version}{25}
\begin{itemize}
	\item If treatment time is $t^*$, estimate a model of the form $y_{it}=\beta_i + \beta_t + Treated_{i} \times \sum_{\substack{t}} \beta_z  I\mathbbm(t-t^*=z)  + \epsilon_{it}$.
	\item Ideally, you will see that coefficients on indicators prior to the treatment ($\beta_z$ for $z<0$) are small and not statistically significant.
	\item If coefficients on post-treatment indicators ($\beta_z$ for $z\geq0$) are statistically significant, that indicates the treatment had an effect.
\end{itemize}
\divider

\step{3}{``Diff in Diff'' Version}{30}
\begin{itemize}
	\item Regress a model of the form $y_{it}=\beta_i + \beta_t + \beta_{DD} \mathit{Treated}_{i} \times \mathit{After}_t + \epsilon_{it}$.
	\item $Treated_i=1$ if unit is treated; $After_t=1$ if time is after treatment.
	\item The difference-in-differences effect is $\beta_{DD}$.
\end{itemize}
\divider


\clearpage

\need[otherinfo]{Sources}

\nocite{*}

\printbibliography


\divider


%% If the NEXT page doesn't start with a \need but you'd
%% still like to add a sidebar, then use this command on THIS
%% page to add it. The optional argument lets you pull up the
%% sidebar a bit so that it looks aligned with the top of the
%% main column.
% \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}
